%************************************************
\chapter{Introduction}\label{ch:introduction}
%************************************************
\begin{refsection}[referencesCh1]
%\section{Rationale}
%
%\section{Problem statement: Overview of the nutrient pullution challenge}
%
%\subsection{Phosphorus pollution}
%
%\subsubsection{Sources}
%
%\paragraph{Livestock industry}
%\paragraph{Fertilizers application}
%\paragraph{Municipal wastewater}
%\paragraph{Industrial wastewater}
%
%\subsubsection{Environmental impacts}
%
%\paragraph{Freshewater}
%\paragraph{Marine water}
%\paragraph{Greenhouse gases emissions}
%
%\subsubsection{Approaches for the abatement of phosphorus pollution}
%
%
%\subsection{Nitrogen pollution}
%
%\subsubsection{Sources}
%\paragraph{Livestock industry}
%\paragraph{Fertilizers application}
%\paragraph{Municipal wastewater}
%\paragraph{Industrial wastewater}
%
%\subsubsection{Environmental impacts}
%
%\paragraph{Freshewater}
%\paragraph{Marine water}
%\paragraph{Greenhouse gases emissions}
%
%\subsubsection{Approaches for the abatement of nitrogen pollution}
%
%\section{Aims and scope}



%\section{Modeling approaches}
%\subsection{Process modeling}
%\subsection{Environmental geographical analysis}
%\subsection{Multi-criteria decision analysis}

\section{Rationale: Overview of the nutrient pullution challenge}
Human population is experiencing a continuous growth since end of the Black Death in the XIV century \citep{biraben1980essay}, which is at 7.8 billion as of 2020, and it is estimated to be at 9.7 billion and 10.9 billion by 2050 and 2100 respectively \citep{UNPopulationProspects}. Population growth demands increasing amounts of food, which in turn requires an efficient food production system to support this growth. In this context, the development of different technical advancements has been a key factor to increase the productivity of the food production system. Notably, crucial developments were achieved in the late modern period\footnote{The terminology used in this dissertation for the periodization of human history follows the English-language historiographical approach. It should be noted that the late modern period is referred to as the contemporary period in the European historiographical approaches.}, including the commercial production of phosphate in 1847 \citep{Samreen2019}, the development of the Haber-Bosch process for the production of synthetic nitrogen-based fertilizers in 1913 \citep{smil1999detonator}, and the mechanization of agriculture and the development of the modern intensive farming in the XX century \citep{constable2003century,nierenberg2005happier}.

Despite these advancements have increased the productivity of agriculture and farming industries, multiple environmental impacts associated with them emerges, including water scarcity, greenhouse gases emissions, nutrient pollution of waterbodies, and soil degradation, among others. These threats must be carefully addressed in order to avoid the depletion of natural resources and reach a sustainable food production system.

Focusing on the impacts derived from agriculture and farming on the nutrient cycles, it can be observed that the natural cycles of phosphorus and nitrogen have been altered these activities \citep{Bouwman2009}. Large amounts of nutrients are released into the environment in the form of synthetic fertilizers and livestock manure. Nitrogen and phosphorus are accumulated in soils, creating a nutrient legacy that is further transported to waterbodies by runoff. This process results in the eutrophication of waters, which can lead algal bloom episodes. Algal blooms are events resulting from the rapid increase of algae in a water system which can be promoted by an excess of nutrients in water, altering the normal functioning of the aquatic ecosystem. Some algal blooms can releases toxins, and they cause hypoxia as a consequence of the aerobic degradation of algal biomass by bacteria.

In addition to the environmental problems, the use of nutrients for food production also raises geopolitical concerns since phosphorus is one to the most sensitive elements to depletion. Phosphorus is a non-renewable material whose reserves are expeted to be depleted in the next 50 to 100 years, and no substitute material is currently known \citep{cordell2009story}. Conversely, synthetic nitrogen can be produced using the atmospheric N\textsubscript{2} as raw material through the Haber-Bosh process. However, nowadays this process relies on non-renewable energy sources, and therefore the production of synthetic nitrogen--based fertilizers is dependent on non-renewable resources as well.

Considering the two challenges described, i.e., nutrient pollution of waterbodies as a consequence of agricultural and farming activities, and the current dependency on non-renewable resources for the production of synthetic fertilizers, nutrient recovery and recycling is not only a desirable but also a necessary approach to develop a sustainable agricultural techniques and ensure the global food security.

Attending to the nutrient releases from livestock intensive farming facilities, known as concentrated animal feeding operations (CAFOs)\footnote{CAFO is a regulatory term defined by the US Environmental Protection Agency for large facilities where animals are kept and raised in confined situations \citep{animal_unit_definition}. This term will be used throughout the dissertation to denote the intensive livestock farming facilities studied.}, several manure management techniques are currently used. The land application of manure is a common technique that allows the recycling of nutrients as fertilizers for crops \citep{Kellog2010}. However, the increase of intensive livestock farming generates vast amounts of waste generated by CAFOs, e.g., each adult cow generates between 28 and 39 kg of manure per day, and each adult pig generates around 11.5 kg of manure per day \citep{USDAHandbook}. Commonly, manure management is based on the separation of liquid and solid phases. The liquid phase can be treated in anaerobic and/or aerobic lagoons for organic matter and pathogens removal, as well as odor control \citep{tilley2014compendium}. The obtained effluent can be used for irrigation and nutrient supplementation of crops.  The solid phase can be composted for the degradation of organic matter and pathogens removal, resulting in a solid material called compost with a larger amount of nitrogen and phosphorus available for plants, which is result of the mineralization of nutrients previously contained in organic compounds. Since compost is also a good source of organic matter for crops, it is a valuable material suitable for sale \citep{tilley2014compendium}. However, both materials, the liquid effluent obtained from the lagoons, and compost, are too bulky to be economically transported to nutrient deficient locations \citep{burns2002phosphorus}. As a result, livestock waste is usually spread in the surroundings of livestock facilities, at a detrimental cost of environment. This result in the gradual build-up of nutrients in croplands, which might lead the harmful environmental impacts previously described.

Therefore, the implementation of processes for the recovery of phosphorus and nitrogen at CAFOs is a promising alternative for abating nutrient releases and reducing the environmental footprint of livestock industry, at the time that valuable nutrient-rich materials are obtained for the redistribution of phosphorus and nitrogen to nutrient-deficient areas. There exist a number of processes for nutrient recovery from livestock waste, which can be differentiated into those technologies oriented to phosphorus recovery, including struvite precipitation, calcium-based precipitates production, coagulation-flocculation, electrochemical processes, and systems based ob phases separation; and processes focused on nitrogen recovery, such as stripping, membrane separation, waste drying coupled with ammonia scrubbing, and phases separation processes. We note that anaerobic digestion is an additional process that can be integrated for manure treatment if the generation of biomethane is pursued, and for increasing the amount of recoverable nutrients through the partial mineralization of nutrients contained in organic compounds. It must be noted that only phosphorus and nitrogen in inorganic compounds can be taken by plants, and therefore the recovery of inorganic nutrients will be the target of the processes studied in this thesis.




\section{Scope and objectives of the thesis}
This thesis seeks to promote the recovery and recycling of nutrients contained in livestock waste by identifying the most appropriate technologies for phosphorus and nitrogen recovery at cattle and swine CAFOs, assessing the potential nutrient releases abatement that could be achieved by the deployment of these systems and analyzing incentive policies for their effective implementation at livestock facilities. Moreover, we introduce a systematic framework for evaluating and selecting the most suitable nutrient recovery system at CAFOs considering geospatial environmental vulnerability to nutrient pollution. 
\paragraph{Objective I:} To perform a review of the state-of-the-art of the processes for phosphorus and nitrogen recovery from livestock waste, identifying those processes whose implementation at CAFOs is feasible from a techno-economic perspective.
\paragraph{Objective II:} To identify environmental indicators for nutrient pollution, and use  them to  assess the potential for the abatement of phosphorus releases by deploying the processes previously selected at livestock facilities at subbasin spatial resolution.
\paragraph{Objective III:} To develop a decision-support system for the evaluation and selection of nutrient recovery systems at livestock facilities integrating techno-economic data of the nutrient recovery technologies and environmental vulnerability to nutrient pollution information determined through a tailored geographic information system (GIS) in order to select  the most suitable system for each particular livestock facility.
\paragraph{Objective IV:} To design and analyze potential incentive policies for the deployment of phosphorus recovery technologies at livestock facilities, as well as to study the fair allocation of limited monetary resources.

\section{Thesis outline}
This dissertation is structured in three parts. Part I is devoted to the study of phosphorus management and recovery, Part II address a techno-economic assessment of the technologies for nitrogen recovery, and Part III conduct a research for determining the best combination of units for biomethane production in order to integrate biogas production and nutrient recovery processes.

\subsection{Part I - Phosphorus management and recovery}
\paragraph{Chapter \ref{ch:PhosphorusTechs} - Technologies for phosphorus recovery.} This chapter performs a review of the main processes for phosphorus recovery from livestock waste, identifying the most promising processes to be deployed at CAFOs using a mixed-integer nonlinear programming model.

\paragraph{Chapter \ref{ch:Struvite} - Assessment of phosphorus recovery through struvite precipitation.} This chapter study the mitigation of phosphorus releases through the deployment of struvite precipitation systems in the watersheds of the contiguous Unites States. Specific surrogate models to predict the production of struvite and calcium precipitates from cattle leachate were developed based on a detailed and robust thermodynamic model. In addition, the variability in the organic waste composition is captured through a probability framework based on Monte Carlo method.

\paragraph{Chapter \ref{ch:Tool} - Geospatial environmental and techno-economic framework for sustainable phosphorus management at livestock facilities.} This chapter presents a decision support framework, COW2NUTRIENT (Cattle Organic Waste to NUTRIent and ENergy Technologies), for the assessment and selection of phosphorus recovery technologies at CAFOs based on environmental information on nutrient pollution and techno-economic criteria. This framework combines eutrophication risk data at subbasin level and the techno-economic assessment of six state-of-the-art phosphorus recovery processes in a multi-criteria decision analysis (MCDA) model. We aimed to provide a useful framework for the selection of the most suitable P recovery system for each particular CAFO, and for designing and evaluating effective GIS-based incentives and regulatory policies to control and mitigate nutrient pollution of waterbodies.

\paragraph{Chapter \ref{ch:Policies} - Analysis of incentive policies for phosphorus recovery.} This chapter conduct a research on the design and analysis of incentive policies using the COW2NUTRIENT framework for the implementation of phosphorus recovery technologies at CAFOs minimizing the negative impact in the economic performance of CAFOs. Moreover, the fair allocation of monetary resources when the available budget is limited is studied using the Nash allocation scheme.

\subsection{Part II - Nitrogen management and recovery}
\paragraph{Chapter \ref{ch:NitrogenTechs} - Multi-scale techno-economic assessment of nitrogen recovery systems for swine operations.} This chapter performs a review of the main processes for nitrogen recovery at intensive swine operations. A multi-scale techno-economic analysis is performed to estimate the capital and operating costs for different treatment capacities, identifying the most promising processes.

\subsection{Part III - Nitrogen management and recovery}
\paragraph{Chapter \ref{ch:BiogasUpgrading} - Optimal technology selection for the biogas upgrading to biomethane.} This chapter performs a systematic study of different biogas upgrading to biomethane processes in order to identify the optimal process attending to the particular characteristics of the biogas produced from livestock manure. Food waste and wastewater sludge are also included for comparison. We aimed to determine the optimal biomethane production processes for the potential combination of biomethane production and nutrient recovery processes into an integrated resources recovery facility.
%The case study demonstration consists of implementing and assessing the sustainable performance of nutrient and energy recovery at 2,217 CAFOs located in the U.S. Great Lakes area (i.e., Minnesota, Indiana, Ohio, Pennsylvania, Wisconsin, and Michigan).

%technic, economic, and environmental dimensions of nutrient recovery at CAFOs have been integrated in a decission support system 
\section*{Bibliography}
\addcontentsline{toc}{section}{Bibliography}

\printbibliography[heading=none]
\end{refsection}